\mytitle{}

### 2018-07-11 paper/paper.tex
Better math

?? Include some details of function approximation in the formalisation? I.e. tile coding, stability and convergence guarantees...

There exists immense variation in \emph{how} policies and/or values may be learned, reliant upon the particular convergence guarantees required.

@@

\subsection{Topology}
The network itself is tree-structured, where one server connects through a dedicated switch to $k$ team leader switches, each connected to $l$ intermediate switches, which in turn each connect to $m$ egress switches.
Agents are co-located with these egress switches, who control the proportion of upstream packets from $n$ external hosts to discard according to load statistics observed along their path to the server.
Agents communicate with their co-hosted OpenFlow-enabled switches---running a modified version of \emph{Open vSwitch} (OVS) \cite{open-vswitch}---to install probabilistic packet-drop rules.
Each link has a delay of \SI{10}{\milli\second}.
All links have unbounded capacity, save for the server-switch connection which is capped at a fixed $U_s$ \si{\mega\bit\per\second} in both directions.

@@

?? Specify update rules here? Semi-gradient Sarsa \cite[pp.\ \numrange{243}{244}]{RL2E}? enhanced by tile-coding with identical parameter choices \cite{DBLP:phd/ethos/Malialis14}.

\begin{subequations}
\begin{align}
\delta_t = R_{t+1} + \gamma \acval{S_{t+1}}{A_{t+1}}{\wvec{t}} - \acval{S_t}{A_t}{\wvec{t}},\\
\bm{w}_{t+1} = \bm{w}_{t} + \alpha \delta_t \nabla{\acval{S_t}{A_t}{\wvec{t}}},
\end{align}
\end{subequations}
observing that the gradient is the binary vector of tile activations.

The reward functions as I specify them here were introduced by \textcite{DBLP:journals/eaai/MalialisK15}; in particular, I make use of the global reward as a performance metric and the \emph{coordinated team learning} (CTL) reward for training.
Using the Iverson bracket notation:
\begin{subequations}
\begin{align}
c_t^{\mathit{f}} = [ > U_s],\\
c_t^{\mathit{tf}} = [ > U_s/k],\\
R_{t}^{\mathit{Global}} = (1 - c_t^{\mathit{f}})\frac{a}{b} - c_t^{\mathit{f}},\\
R_{t}^{\mathit{CTL}} = (1 - c_t^{\mathit{f}}c_t^{\mathit{tf}})\frac{a}{b} - c_t^{\mathit{f}}c_t^{\mathit{tf}},
\end{align}
\end{subequations}

?? Note, these are dependent on the current agent! Need to find a succinct way to express this somehow...

>>>>

%?? Include some details of function approximation in the formalisation? I.e. tile coding, stability and convergence guarantees...

There exists immense variation in \emph{how} policies and/or values may be learned, reliant upon the learning environment, problem and required convergence guarantees.
In particular, we shall focus on methods which choose actions according to their value estimates from the current state.
To cope with a continuous state- and/or action-space, one valuable technique is to employ \emph{tile-coding} \cite[pp.\ \numrange{217}{221}]{RL2E}---this converts our state from $\mathbb{R}^d \times A$ into a sparse boolean feature vector $\operatorname{\mathbf{x}}(s, a) \forall a \in \mathcal{A}$ by subdividing it into a number of overlapping $d$-dimensional grids with an optional bias component.
This transform, as an example of linear function approximation, then necessitates the use of \emph{semi-gradient Sarsa} \cite[pp.\ \numrange{243}{244}]{RL2E}.
Given a weight vector $\wvec{0}=\bm{0}$ which defines :
\begin{subequations}
	\begin{gather}
	\acval{s}{a}{\wvec{}} = \wvec{}^{\top} \operatorname{\mathbf{x}}(s, a),\\
	\delta_t = R_{t+1} + \gamma \acval{S_{t+1}}{A_{t+1}}{\wvec{t}} - \acval{S_t}{A_t}{\wvec{t}},\\
	\bm{w}_{t+1} = \bm{w}_{t} + \alpha \delta_t \nabla{\acval{S_t}{A_t}{\wvec{t}}}.
	\end{gather}
	\label{eqn:sg-sarsa}
\end{subequations}

Observing that $\nabla{\acval{\cdot}{\cdot}{\cdot}} = \operatorname{\mathbf{x}}(s, a)$, and $\operatorname{\mathbf{x}}(s, a)$ .
Furthermore, if the action set remains

@@

\subsection{Topology}
The network itself is tree-structured, where one server $s$ connects through a dedicated switch to $k$ team leader switches, each connected to $l$ intermediate switches, which in turn each connect to $m$ egress switches.
Agents are co-located with these egress switches, who control the proportion of upstream packets from $n$ external hosts to discard according to load statistics observed along their path to the server.
Agents communicate with their co-hosted OpenFlow-enabled switches---running a modified version of \emph{Open vSwitch} (OVS) \cite{open-vswitch}---to install probabilistic packet-drop rules.
Each link has a delay of \SI{10}{\milli\second}.
All links have unbounded capacity, save for the server-switch connection which is capped at a fixed $U_s$ \si{\mega\bit\per\second} in both directions.

@@

Agents receive state input from monitors in the environment, a vector of load values (in \si{\mega\bit\per\second}) observed along their path to $s$: this is tile-coded with identical parameter choices to those of \textcite{DBLP:phd/ethos/Malialis14}.

At every time step, each agent installs an action onto the switch which hosts it, instructing it to drop $p\si{\percent}$ of traffic.

The reward functions as I specify them here were introduced by \textcite{DBLP:journals/eaai/MalialisK15}; in particular, I make use of the global reward as a performance metric and the \emph{coordinated team learning} (CTL) reward for training.
These assume the presence of a classifier (exact or heuristic) which estimates the volume of `legitimate traffic' received at any point, $g(\cdot)$.
At time $t$ an agent $a$ (with team leader $l_a$) receives either $R_{t}^{\mathit{Global}}$ or $R_{t}^{\mathit{CTL}}$:
\begin{subequations}
\newcommand{\cond}[2]{\operatorname{c}_{#1,t}#2}
\newcommand{\load}[1]{\operatorname{load}_{t}(#1)}
\begin{gather}
\cond{f} = [\load{s} > U_s],\\
\cond{c}{(a)} = [\load{l_a} > U_s/k],\\
R_{t}^{\mathit{Global}} = (1 - \cond{f}) \frac{g(\load{s})}{g(\load{\mathit{total}})} - \cond{f},\\
R_{t}^{\mathit{CTL}} = (1 - \cond{f}\cond{c}{(a)}) \frac{g(\load{l_a})}{g(\load{\mathit{team}})} \allowbreak - \cond{f} \cond{c}{(a)},
\end{gather}
where $\load{\mathit{total}}$ and $\load{\mathit{team}}$ refer to the load across all egress points in the network and in $a$'s team, respectively.
\end{subequations}

The tile-coded state and chosen reward function are then used as input for the \emph{semi-gradient Sarsa} algorithm described in \cref{eqn:sg-sarsa}.
